NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-12-22 results.tex
update on bib and typos

Finally, in Figure \ref{fig:aaa:dphi} we show the azimuthal 
separation $\Delta\phi$ between all three diphoton pairs. 
Similar features as before are visible as both the NLO QCD 
and NLO EW corrections relax the kinematic boundaries of 
the leading order calculation.Especially the azimuthal separation of the leading and 
third leading photon receives substantial shape corrections 
throughout the entire spectrum, with and without the 
presence of a jet veto. The angular distribution between leading photon
and the second or third subleading photon exhibit a kinematical edge at $\pi/2$ which 
is relaxed at NLO. 
This kinematical edge can be understood in the following way:
 Let us consider the first observable, the angular separation between 
the leading and the subleading photon, the argument also holds for the separation between
the leading and the third leading photon. The third leading photon has to recoil against the
system of the two leading photons. Let us go into the limit where the three photons have
a very similar transverse momentum and consider the configuration where the leading
photon is back-to-back to the third leading photon. Then the second photon must 
be perpendicular to this axis. If the third photon has less transverse momentum, it 
needs the second photon to recoil against the leading photon. Therefore it gets closer
to the third photon and further away from the leading photon. $\pi/2$ is therefore the
minimal distance the second photon can have to the leading one.  Only at NLO where
one can have additional radiation this constraint is relaxed. 
\revised{Therefore on finds that for the distributions involving the leading photon the particles
tend to be in a back-to-back configuration. This is most pronounced for the separation between
the two hardest photons and gets step by step relaxed by replacing the subleading by the third leading
photon and the leading by the subleading respectively.} We will see later in Fig.
\ref{fig:aaz:dphi} that this situation is also present when one replaces one of the subleading
photons by a $Z$ boson. 
The electroweak corrections are negligible for this 
observable.

@@

Figure \ref{fig:aaz:myy} continues to display the invariant masses 
of the leading and subleading photon, and both the leading and 
subleading photon and the lepton pair. \revised{For the invariant mass of the
two leading photons one also observes a shift towards higher invariant masses
in the presence of QCD corrections as seen in Fig. \ref{fig:aaw:myy}. The effect
is less pronounced due to the fact that there is also a triple photon process contributing
to the dilepton final state. The observed pattern is therefore a mixture between what
can be seen in Fig. \ref{fig:aaa:myy} and the results in Fig. \ref{fig:aaw:myy}.}
The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ at the $Z$ boson mass 
is produced by 
configurations where the respective photon is emitted by the 
lepton-pair from a resonant $Z$ boson decay. 
Again, the QCD corrections are moderate, always staying below 
$\deltaQCD=0.4$ and of a similar shape as encountered already in 
\aaw\ production. 
The jet veto again reduces the QCD corrections and drives them negative 
in large portions of the observable range, reaching as much as 
$\deltaQCD=-0.5$ for the diphoton invariant mass. 
The electroweak corrections, on the other hand, are qualitatively very similar 
to the \aaw\ case: with the exception of the well known positive 
radiative corrections below the $Z$ peak, they are negative 
throughout, reaching $\deltaEW=-20\%$ at invariant masses of 
1\,TeV.
As in the case of the transverse momenta, due to the similar size 
of the QCD and electroweak corrections at large transverse 
momenta, the difference between their additive and the multiplicative 
combination is amplified.

>>>>

Finally, in Figure \ref{fig:aaa:dphi} we show the azimuthal 
separation $\Delta\phi$ between all three diphoton pairs. 
Similar features as before are visible as both the NLO QCD 
and NLO EW corrections relax the kinematic boundaries of 
the leading order calculation.Especially the azimuthal separation of the leading and 
third leading photon receives substantial shape corrections 
throughout the entire spectrum, with and without the 
presence of a jet veto. The angular distribution between leading photon
and the second or third subleading photon exhibit a kinematical edge at $\pi/2$ which 
is relaxed at NLO. 
This kinematical edge can be understood in the following way:
 Let us consider the first observable, the angular separation between 
the leading and the subleading photon, the argument also holds for the separation between
the leading and the third leading photon. The third leading photon has to recoil against the
system of the two leading photons. Let us go into the limit where the three photons have
a very similar transverse momentum and consider the configuration where the leading
photon is back-to-back to the third leading photon. Then the second photon must 
be perpendicular to this axis. If the third photon has less transverse momentum, it 
needs the second photon to recoil against the leading photon. Therefore it gets closer
to the third photon and further away from the leading photon. $\pi/2$ is therefore the
minimal distance the second photon can have to the leading one.  Only at NLO where
one can have additional radiation this constraint is relaxed. 
\revised{Therefore, one finds that for the distributions involving the leading photon the particles
tend to be in a back-to-back configuration. This is most pronounced for the separation between
the two hardest photons and gets step by step relaxed by replacing the subleading by the third leading
photon and the leading by the subleading respectively.} We will see later in Fig.
\ref{fig:aaz:dphi} that this situation is also present when one replaces one of the subleading
photons by a $Z$ boson. 
The electroweak corrections are negligible for this 
observable.

@@

Figure \ref{fig:aaz:myy} continues to display the invariant masses 
of the leading and subleading photon, and both the leading and 
subleading photon and the lepton pair. \revised{For the invariant mass of the
two leading photons one also observes a shift towards higher invariant masses
in the presence of QCD corrections as seen in Fig.\ \ref{fig:aaw:myy}. The effect
is less pronounced due to the fact that there is also a triple photon process contributing
to the dilepton final state. The observed pattern is therefore a mixture between what
can be seen in Fig.\ \ref{fig:aaa:myy} and the results in Fig.\ \ref{fig:aaw:myy}.}
The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ at the $Z$ boson mass 
is produced by 
configurations where the respective photon is emitted by the 
lepton-pair from a resonant $Z$ boson decay. 
Again, the QCD corrections are moderate, always staying below 
$\deltaQCD=0.4$ and of a similar shape as encountered already in 
\aaw\ production. 
The jet veto again reduces the QCD corrections and drives them negative 
in large portions of the observable range, reaching as much as 
$\deltaQCD=-0.5$ for the diphoton invariant mass. 
The electroweak corrections, on the other hand, are qualitatively very similar 
to the \aaw\ case: with the exception of the well known positive 
radiative corrections below the $Z$ peak, they are negative 
throughout, reaching $\deltaEW=-20\%$ at invariant masses of 
1\,TeV.
As in the case of the transverse momenta, due to the similar size 
of the QCD and electroweak corrections at large transverse 
momenta, the difference between their additive and the multiplicative 
combination is amplified.
